The Ontological Modal Collapse \\ as a Collapse of the Square of Opposition

### 2014-09-10 Papers/Universalis/ModalCollapse.tex
Fix issue described in footnote 3

Moreover, in any modal logic where the axiom \textbf{T} holds
(i.e. where the accessibility relation is reflexive), a total collapse
of the modalities (\textbf{MC''}) occurs.\footnote{C.: I am a bit lost here. Do you want to
  say that any logic that includes T strongly collapses? This would be 
  odd. Where is the theorem in the Isabelle file(s) that proves this? Also: MC'' should
  be stated more precisely, I mean like: $((\varphi \biimp \nec \varphi) \wedge (\nec \varphi
  \biimp \pos \varphi))$.}  Interestingly, under this stronger form of modal
  collapse, the contraries entail their subcontraries even without the
  existential import.

@@

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[\textbf{MC}] Everything that is the case is so necessarily:
  $\hol{\allq \phi [\phi \imp \nec \phi]}$ \\
\item[\textbf{MC'}] Everything that is possible is necessary:
  $\hol{\allq \phi [\pos \phi \imp \nec \phi]}$  \\
\item[\textbf{T}] Everything that is necessary is the case:
  $\hol{\allq \phi [\nec \phi \imp \phi]}$ \\
\item[\textbf{ExImp}] (Modal Existential Import):
  $\hol{\pos \top}$ \\
\item[\textbf{AI}] Everything that is necessary is possible:
  $\hol{\allq \phi [\nec \phi \imp \pos \phi]}$ \\
\item[\textbf{MC''}] Modalities collapse completely:
  $\hol{\allq \phi [\phi \biimp \pos \phi \biimp \nec \phi]}$
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Modal Collapse}
\label{fig:collapse} 
\end{figure}

>>>>

Moreover, in any modal logic where the axiom \textbf{T} holds
(i.e. where the accessibility relation is reflexive), 
even a total collapse of the modalities (\textbf{MC''}) 
is entailed by \textbf{MC}.
Interestingly, under this stronger form of modal
collapse, the contraries entail their subcontraries even 
without the existential import.

@@

\begin{figure}[t]
\noindent \framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[\textbf{MC}] Everything that is the case is so necessarily:
  $\hol{\allq \phi [\phi \imp \nec \phi]}$ \\
\item[\textbf{MC'}] Everything that is possible is necessary:
  $\hol{\allq \phi [\pos \phi \imp \nec \phi]}$  \\
\item[\textbf{T}] Everything that is necessary is the case:
  $\hol{\allq \phi [\nec \phi \imp \phi]}$ \\
\item[\textbf{ExImp}] (Modal Existential Import):
  $\hol{\pos \top}$ \\
\item[\textbf{AI}] Everything that is necessary is possible:
  $\hol{\allq \phi [\nec \phi \imp \pos \phi]}$ \\
\item[\textbf{MC''}] Modalities collapse completely:
  $\hol{\allq \phi [(\phi \biimp \nec \phi) \wedge (\pos \phi \biimp \nec \phi)]}$
\end{itemize}
\end{minipage}
} \vskip-.5em
\caption{Modal Collapse}
\label{fig:collapse} 
\end{figure}
